Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-18 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polished section of methodology

We find buildings which will be too close at time $t$
and aggregate the buildings in the same group by introducing bridges.
We grow the (bridged) original buildings by buffering with miter joins.
Our building simplification consists of two steps.
The first one is to use dilation and erosion to remove pits and spikes.
The second step is to remove vertices using Imai--Iri algorithm.
To make sure that the intermediate-scale buildings never shrink,
we merge the shape of a building 
with the shape at the previously immediate step. 
Also, we clip the building using the shape on goal map.

Our grouping is based on growing, aggregating and some of simplifying. 
So we present the three operators before grouping.

\subsection{Growing buildings by buffering}
\label{sec:Grow}
We grow buildings based on buffering. 
There are two typical ways of buffering a polygon, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way to
better preserve the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if a vertex of the 
buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
Distance $\dtrm{G}$ is the growth at time $t$.
We denote by $d_\mathrm{G}$ the growth for goal map.
Then we define
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_TwoKinds}
	\caption{Buffering a polygon using different kinds of joins.}
	\label{fig:Buffer_TwoKinds}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_MiterLimits}
	\caption{}
	\label{fig:Buffer_MiterLimits}
\end{figure}

\subsection{Simplifying grown buildings based on dilation and erosion}
\label{sec:DilationErosion}
\citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the directions of the buildings have to be 
concerned.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
We use a method based on buffering to remove pits and spikes of buildings.
Our method is slightly different than \citet{Meijers2016},
but there is an available library \textsc{Clipper} \citep{Johnson2014} 
for the operations.
\fig\ref{fig:RemovePitAndSpike} illustrates our buffering-based method.
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

At time $t$, we grow buildings with distance $\dtrm{G}$,
dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with distance $\dtrm{E}$.
A problem we may have is that 
a building may be broken by eroding
(see \fig\ref{fig:ErosionBreak} for example).
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but can be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and the building is not thick enough, 
the thin part may disappear.
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

\begin{figure}[tb]
	\centering
	\includegraphics[]{ErosionBreak}
	\caption{Dilate the gray polygon, then erode the dilated polygon.
		(a) Dilate and erode with distance $d_1$.
		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
		In (a) the result of dilation and erosion is the same as the original 
		polygon, while in (b) the result consists of two parts.
	}
	\label{fig:ErosionBreak}
\end{figure}

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we set erosion distance
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

@@

We aggregate buildings if they become too close because of growing.
Our basic idea is to add bridges between buildings
(see for example \fig\ref{fig:GrowAndBridge}).

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Aggregate original buildings in the same group by introducing 
		bridges.
		Then grow the bridged buildings.}
	\label{fig:GrowAndBridge}
\end{figure*}

We grow each original building and, as illustrated in 
\sect\ref{sec:DilationErosion}, simplify the grown building.
If some buildings become too close after these operations,
we aggregate them by adding bridges.
Following \citet{Stoter2009}, 
we define that two buildings are too close if their distance is less than
$\epsilon= 0.2\,\mathrm{mm}$ on map.
The real separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

Our way of detecting close buildings is simple.
We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins.
We merge the buffers that overlap each other.
The buildings intersect with the same merged buffer 
are identified as a group of close buildings.
According to the group of buildings, 
we find the group of corresponding original buildings.
For each pair of the original buildings in a group,
we connect them by adding a line segment linking the nearest points.
The line segments for the group of original buildings may cross each other or 
even intersect buildings.
To make the topology simple, 
we only select some of the line segments as \emph{bridges}.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are identified as bridges.
We aggregate the group of original buildings by adding these bridges.

Aggregated buildings may become too close after growing because of bridges.
\fig\ref{fig:BridgeMoreBuilding} shows such an example.
We grow and buffer buildings $p$, $q$, and~$r$.
As the buffers of $q$ and~$r$ overlap with each other
(see \fig\ref{fig:BridgeMoreBuilding}c),
we aggregated buildings $q$ and~$r$ by adding a bridge.
There are two buildings left in \fig\ref{fig:BridgeMoreBuilding}d.
Because of the bridge, when we grow and buffer the buildings in 
\fig\ref{fig:BridgeMoreBuilding}d, 
the buffer of building $p$ overlap with the buffer of the bridged $q$ and $r$
(see \fig\ref{fig:BridgeMoreBuilding}f).
We aggregate building $p$ with bridged $q$ and $r$
(see \fig\ref{fig:BridgeMoreBuilding}g).
There is one building left in \fig\ref{fig:BridgeMoreBuilding}g.
Then we grow and buffer again.
There is one building left after this process.
The number of buildings does not decrease comparing to last process.
The iteration stops.

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{BridgeMoreBuilding}
	\caption{Iteratively aggregating close buildings by adding bridges.
		(a) original buildings $p$, $q$, and~$r$.
		(b) grow the original buildings with distance $\dtrm{G}$.
		(c) buffer the grown buildings with distance $d_{\epsilon,t}/2$ using 
		round joins.
		(d) aggregate buildings $q$ and~$r$ by adding a bridge,
		as their buffer overlap with each other in (c).
		(e) grow the buildings in (d) with distance $\dtrm{G}$.
		(f) buffer the grown buildings in (e) with distance $d_{\epsilon,t}/2$ 
		using round joins.
		(g) aggregate buildings $p$, $q$ and~$r$ by adding bridges.
		(h) grow the buildings in (g) with distance $\dtrm{G}$.
		(i) buffer the grown buildings in (h) with distance $d_{\epsilon,t}/2$ 
		using round joins.
	}
	\label{fig:BridgeMoreBuilding}
\end{figure}

@@

%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%\begin{equation}
%\label{eq:d_epsilont2}
%d_{\epsilon, t} = \epsilon \cdot M_t.
%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least $d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap with each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{NearestPoints}
%	\caption{The nearest points between a pair of buildings may change because 
%		of growing. 
%		The two squares and the two circles respectively mark
%		the nearest points before and after growing.
%	}
%	\label{fig:NearestPoints}
%\end{figure}

@@

We simplify the buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
First, this algorithm finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline 
and has the least number of line segments, with error smaller than $d_{l,t}$.

@@

We add two more constraints for a shortcut to be valid. 
First, a shortcut must be completely inside the grown building.
If a shortcut is outside,
we are not able to arrive at the shortcut by growing.
Second, a shortcut is not allowed to intersect with the aggregated building.
If we allow this intersection, 
the building will have to be shrunk. 
Of course, we do not want to shrink.
\todo{a shortcut is not allowed to intersect with the building at the 
	immediately previous step?}

@@

%\subsection{Grouping buildings based on buffering}
%\label{sec:Group}
%There are many research works about grouping buildings.
%\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
%However, our two needs, 
%the distances between buildings are always larger than a specified threshold 
%and small bays should be removed, 
%motivate us to develop our own grouping method.
%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%%\begin{equation}
%%\label{eq:d_epsilont}
%%d_{\epsilon, t} = \epsilon \cdot M_t.
%%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least $d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap with each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{CloseDetect}
%	\caption{Group buildings based on buffering.
%		(a) original buildings.
%		(b) bridges detected to aggregate the three buildings.
%		(c) grow the original buildings with distance $\dtrm{G}$.
%		(d) buffer the grown buildings in (c) 
%		with distance $d_{\epsilon, t} /2$ using round joins.
%		(e) buffer the original buildings 
%		with distance $\alpha \dtrm{G}+d_{\epsilon, t}/2 $ 
%		using round joins, where $\alpha=1.5$
%		(see \sect\ref{sec:Grow}).
%		(f) according to the buffer in (e), 
%		we put the three original buildings in the same group.
%		We aggregate the original buildings by adding the two bridges 
%		and grow the aggregated building with distance $\dtrm{G}$.
%	}
%	\label{fig:CloseDetect}
%\end{figure}

@@

\subsection{Generating the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We aggregate original buildings (see \sect\ref{sec:Aggregate}).
Then we grow (see \sect\ref{sec:Grow}) 
and simplify 
(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown buildings.
See for example \fig\ref{fig:GrowAndBridge}, 
the building at time $t=1$ is the goal form of the three original buildings of.

>>>>

We find original buildings which will grow to become too close at time $t$
and aggregate them by introducing bridges.
We grow the (bridged) original buildings by buffering with miter joins.
We simplify the grown buildings with two steps.
The first one is to use dilation and erosion to remove pits and spikes.
The second step is to remove vertices using Imai--Iri algorithm.
To make sure that buildings never shrink when $t$ is increasing,
For a building, we merge its shape at time $t$ 
and its shape at the immediately previous step (before $t$). 
Also, we clip the building using the shape on goal map.

Our aggregating relies on growing and dilation-erosion-based simplifying. 
So we present the two operators before aggregating.

\subsection{Growing buildings by buffering}
\label{sec:Grow}
We grow buildings based on buffering. 
We denote by $d_\mathrm{G}$ the growth for goal map.
At time $t$, the growth is
\begin{equation}
	\label{eq:d_Gt}
	\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

There are two typical ways of buffering a polygon, i.e.,
using round joins or using miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
We choose the second way in order to
preserve the right angles of buildings.
If an angle is acute, however, 
an excessively long \emph{spike} will be produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if the tip of a spike 
is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_TwoKinds}
	\caption{Buffering a polygon using round joins and using miter joins.}
	\label{fig:Buffer_TwoKinds}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_MiterLimits}
	\caption{Using square joins instead of miter joins to avoid long spikes.
	}
	\label{fig:Buffer_MiterLimits}
\end{figure}

\subsection{Simplifying grown buildings based on dilation and erosion}
\label{sec:DilationErosion}
\citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the directions of the buildings have to be 
concerned.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
Our method is similar to \citet{Meijers2016}.
We dilate and erode to remove ``dents'' and ``bumps'' of buildings
(see \fig\ref{fig:RemovePitAndSpike}).
The operations of dilation and erosion are available from library 
\textsc{Clipper} \citep{Johnson2014}.

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemovePitAndSpike}
	\caption{Removing a dent by dilating and then remove a bump by eroding.
		(a) a polygon with a dent and a bump;
		(b) dilating the polygon in (a) with distance $d$ to remove the dent;
		(c) eroding the polygon in (b) with $2d$ to remove the bump;
		(d) dilating the polygon in (c) with $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

At time $t$, we grow buildings with distance $\dtrm{G}$.
We dilate with distance $\dtrm{D}$ ($\dtrm{D}>0$),
erode with $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with $\dtrm{E}$.
A problem we may have is that 
a building may be broken by eroding
(see \fig\ref{fig:ErosionBreak} for example).
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but can be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and the building is not thick enough, 
a thin part may disappear.
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

\begin{figure}[tb]
	\centering
	\includegraphics[]{ErosionBreak}
	\caption{Dilating the gray polygon, then eroding the dilated polygon.
		(a) Dilating and eroding with distance $d_1$.
		(b) Dilating and eroding with $d_2$, where $d_2>d_1$.
		In (a) the result of dilation and erosion is the same as the original 
		polygon, while in (b) the result consists of two parts.
	}
	\label{fig:ErosionBreak}
\end{figure}

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Unfortunately, distance $\dtrm{G}$ can be arbitrarily small 
according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we set erosion distance
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we have to make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we need to make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

@@

We grow each original building and, as illustrated in 
\sect\ref{sec:DilationErosion}, simplify the grown building.
If some buildings become too close after these operations,
we aggregate them by adding bridges
(see for example \fig\ref{fig:GrowAndBridge}).
Following \citet{Stoter2009}, 
we define that two buildings are too close if their distance is less than
$\epsilon= 0.2\,\mathrm{mm}$ on map.
The real separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Aggregating original buildings in the same group by introducing 
		bridges.
		Then grow the bridged buildings.}
	\label{fig:GrowAndBridge}
\end{figure*}

Our way of detecting close buildings is simple.
We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins.
We merge the buffers that overlap each other.
The buildings intersect the same merged buffer 
are identified as a group of close buildings.
The corresponding original buildings 
are identified as a group of original close buildings.
For each pair of the original buildings in the same group,
we connect them by adding a line segment linking the nearest points.
The line segments for a group of original buildings may cross each other or 
even intersect buildings.
To make the topology simple, 
we only select some of the line segments as \emph{bridges}.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are identified as bridges.
We aggregate the group of original buildings by adding these bridges.

Aggregated buildings may become too close after growing because of bridges.
Therefore we have to iterate the process of aggregating.
\fig\ref{fig:BridgeMoreBuilding} shows such an example.
We grow and buffer buildings $p$, $q$, and~$r$.
As the buffers of $q$ and~$r$ overlap
(see \fig\ref{fig:BridgeMoreBuilding}c),
we aggregate buildings $q$ and~$r$ by adding a bridge
(see \fig\ref{fig:BridgeMoreBuilding}d).
There are two buildings left in \fig\ref{fig:BridgeMoreBuilding}d.
We grow and buffer the buildings in 
\fig\ref{fig:BridgeMoreBuilding}d, 
the buffer of building $p$ overlap the buffer of the bridge for $q$ and $r$
(see \fig\ref{fig:BridgeMoreBuilding}f).
We aggregate building $p$ with bridged $q$ and $r$
(see \fig\ref{fig:BridgeMoreBuilding}g).
There is one building left in \fig\ref{fig:BridgeMoreBuilding}g.
Then we grow and buffer again.
There is one building left after this process.
The number of buildings does not decrease comparing to last process.
The iteration stops.

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{BridgeMoreBuilding}
	\caption{Iteratively aggregating close buildings by adding bridges.
		(a) original buildings $p$, $q$, and~$r$.
		(b) growing the original buildings with distance $\dtrm{G}$.
		(c) buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
		using round joins.
		(d) aggregating buildings $q$ and~$r$ by adding a bridge,
		as their buffer overlap each other in (c).
		(e) growing the buildings in (d) with distance $\dtrm{G}$.
		(f) buffering the grown buildings in (e) with distance 
		$d_{\epsilon,t}/2$ using round joins.
		(g) aggregating buildings $p$, $q$ and~$r$ by adding bridges.
		(h) growing the buildings in (g) with distance $\dtrm{G}$.
		(i) buffering the grown buildings in (h) with distance 
		$d_{\epsilon,t}/2$ using round joins.
	}
	\label{fig:BridgeMoreBuilding}
\end{figure}

@@

%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%\begin{equation}
%\label{eq:d_epsilont2}
%d_{\epsilon, t} = \epsilon \cdot M_t.
%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least $d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{NearestPoints}
%	\caption{The nearest points between a pair of buildings may change because 
%		of growing. 
%		The two squares and the two circles respectively mark
%		the nearest points before and after growing.
%	}
%	\label{fig:NearestPoints}
%\end{figure}

@@

We simplify the grown buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
First, this algorithm finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline 
and has the least number of line segments, with error smaller than $d_{l,t}$.

@@

We add two more constraints for a shortcut to be valid. 
First, a shortcut must be completely inside the grown building.
If a shortcut is outside,
we are not able to arrive at the shortcut by growing.
Second, a shortcut is not allowed to intersect the aggregated building.
If we allow this intersection, 
the building will have to be shrunk. 
Of course, we do not want to shrink.
\todo{a shortcut is not allowed to intersect the building at the 
	immediately previous step?}

@@

%\subsection{Grouping buildings based on buffering}
%\label{sec:Group}
%There are many research works about grouping buildings.
%\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
%However, our two needs, 
%the distances between buildings are always larger than a specified threshold 
%and small bays should be removed, 
%motivate us to develop our own grouping method.
%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%%\begin{equation}
%%\label{eq:d_epsilont}
%%d_{\epsilon, t} = \epsilon \cdot M_t.
%%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least $d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{CloseDetect}
%	\caption{Group buildings based on buffering.
%		(a) original buildings.
%		(b) bridges detected to aggregate the three buildings.
%		(c) grow the original buildings with distance $\dtrm{G}$.
%		(d) buffer the grown buildings in (c) 
%		with distance $d_{\epsilon, t} /2$ using round joins.
%		(e) buffer the original buildings 
%		with distance $\alpha \dtrm{G}+d_{\epsilon, t}/2 $ 
%		using round joins, where $\alpha=1.5$
%		(see \sect\ref{sec:Grow}).
%		(f) according to the buffer in (e), 
%		we put the three original buildings in the same group.
%		We aggregate the original buildings by adding the two bridges 
%		and grow the aggregated building with distance $\dtrm{G}$.
%	}
%	\label{fig:CloseDetect}
%\end{figure}

@@

\subsection{Generating the goal shapes of buildings}
\label{sec:Goal}
To generate the goal shapes of buildings, we set time $t=1$.
We aggregate original buildings (see \sect\ref{sec:Aggregate}).
Then we grow (see \sect\ref{sec:Grow}) 
and simplify 
(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown buildings.
See for example \fig\ref{fig:GrowAndBridge}, 
the building at time $t=1$ is the goal shape of the three original buildings.
